\documentclass[10pt]{article}
\usepackage{geometry}
\textheight=8.0in
\pagestyle{empty}
\geometry{hmargin={0.5in,0.5in}}
\geometry{vmargin={0.5in,0.5in}}
\setlength{\parskip}{0in}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\newenvironment{sitemize}{
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}

\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{Andrei Warkentin}  & \\
1215 Johnson dr. \#2622, & 224-241-2080\\
Buffalo Grove, IL, 60089 & andrey.warkentin@gmail.com
\end{tabular*}
\\
\vspace{0.1in}

{\large \textbf{Overview}}
\begin{sitemize}
\item environments: POSIX, Win32, .NET, Android, UEFI,
  NT kernel, Linux kernel, Xen
\item kernels, drivers, firmware, porting / bring-up
\item hardware/software boundary
\item IA-32, AMD64, ARMv7, embedded hardware/buses
\item thorough testing and excellent debugging skills
\item flexible performer, fast learner
\item good, responsible team player
\item Xen, Linux and UEFI TianoCore contributor
\item LinkedIn profile: \texttt{http://www.linkedin.com/pub/andrei-warkentin/1a/320/37}
\end{sitemize}

{\large \textbf{Education}}

\begin{itemize}
\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{University of Illinois at Chicago} & Chicago, IL \\
    Bachelor of Science in Computer Science, 2008 & \\
  \end{tabular*}
  \begin{sitemize}
    \item ACM, LUG member.
    \item ACM@UIC SIGOPS (Operating Systems) founder,
      ACM corporate relations.
    \item 2006 Caterpillar Homeland Security
      Award of Excellence for work in CS.
  \end{sitemize}
\end{itemize}

{\large \textbf{Work History}}
\begin{itemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Principal Staff Software Engineer} & April 2010 - Present\\
    Motorola Mobility, & Libertyville, IL\\
  \end{tabular*}
  \begin{sitemize}
  \item Motorola Xoom (Android 3.0 tablet) bring-up on NVidia Tegra 2 ARMv7 platform.
    Linux kernel porting, debugging, driver development, multimedia bring-up, camera,
    HDMI/HDCP, factory test software.
  \item Motorola Atrix (Android phone) development assistance.
  \item LTE (4G) model firmware (Linux-based) development assistance.
  \item eMMC/SDHCI upstream development for Linux SD/MMC subsystem.
  \item UEFI Tiano Core EDK2 contributor, prototype bring-up on Tegra 2.
  \item UEFI SD/MMC subsystem development.
  \item Google Summer of Code mentor for porting UEFI firmware (EDK2) to
    IA-32/X64 Xen virtual machines.
  \item Performance analysis tools.
  \item Converged Computing Bravo! award.
  \end{sitemize}

 \item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Software Development Engineer} &  July 2008 - March 2010\\
    Microsoft,  & Redmond, WA\\
  \end{tabular*}
  \begin{sitemize}
  \item Position with the Work Anywhere group.
  \begin{sitemize}
  \item Development
    owner for the Roaming User Profile and Folder Redirection components.
  \item Technology investigations and prototyping with the Microsoft Synchronization
    Framework and other user- and kernel-space technologies to explore
    fine-grained synchronization of registry and other user profile data.
  \item
    Prototype registry filter driver for logging registry and
    certain transactional operations.
  \end{sitemize}
  \item Position with the Core Virtualization (Hyper-V)
  group.
  \begin{sitemize}
  \item Component owner for parts of the emulated virtual device
  stack, virtual machine BIOS.
  \item Correctness, stability
    and third-party OS support for Hyper-V emulated virtual devices stack
    and virtual machine BIOS.
  \item Internal tools, mostly in the debugging problem space, to
    facilitate debugging AMI BIOS and UEFI firmware.
  \item Component owner for Virtual Machine UEFI. Device support,
    critical path, memory footprint optimization. Synthetic network
    booting, integration with virtual machine management stack.
    KD debugging support for UEFI, allowing
    source-level debugging via WinDbg and FireWire.
  \item Investigation and prototype implementation of virtual machine device
    emulator isolation.
  \item Intern mentoring for implementing isolated UART emulation.
  \item Patent pending for EFI work, patent pending for
    virtual machine emulator isolation work.
  \item College Recruiting.
  \end{sitemize}
  \end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Software Development Engineer Intern} &  May 2007 - August
    2007\\
    Microsoft,  & Redmond, WA\\
  \end{tabular*}
  \begin{sitemize}
  \item Internship with the Core Virtualization (Hyper-V) group,
    porting the Hyper-V high-performance synthetic device stack to x64
    UEFI firmware.
  \item Hypervisor, VMBus, timer, SCSI and
    framebuffer support, to allow a fully synthetic Windows boot with minimum
    usage of the emulated virtual device stack.
  \end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Software Development Engineer Intern} &  May 2006 - August
    2006\\
    Microsoft,  & Redmond, WA\\
  \end{tabular*}
  \begin{sitemize}
  \item Internship with the Core Virtualizaton (Hyper-V) group,
  porting a Tiano Core (EDK1) UEFI Win32 simulator as stand-alone x64 virtual
  machine firmware capable of booting Windows UEFI-way.
  \item UEFI build tools modifications to generate bootable firmware.
  \item Implementation of ACPI support necessary to boot Windows.
\end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Software
    Engineer} &  May 2005 - May 2008\\
    Data Armor / CHI Networks,  & Chicago, IL\\
  \end{tabular*}
  \begin{sitemize}
  \item Senior system and network administrator for CHI Networks and
    CHI Networks clients.
  \item Development of software supporting system and network
    infrastructure.
  \item Development, QA and testing of network management and
    services product under development.
  \end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{IT Consultant and Research Programmer} & August 2004 -
    August 2005\\
    Academic Computing and Communications Center, \\
    University of Illinois at Chicago,  & Chicago, IL\\
  \end{tabular*}
  \begin{sitemize}
  \item IT support for UIC computer labs, hardware maintenance and
    client support.
  \item Development of internal tools to facilitate network
    installation of software.
  \end{sitemize}
\end{itemize}

{\large \textbf{Experience History}}
\begin{itemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Lead Developer} & August 2007 - July 2008\\
    Ethos Operating System, & \texttt{http://wwww.rites.uic.edu/\~{
    }solworth/ethos.html}\\
  \end{tabular*}
  \begin{sitemize}
  \item Prototype design and implementation of a small kernel running
    on top of the IA-32 Xen Hypervisor, to facilitate research and
    development of a secure OS base.
  \item Initial bring-up work,  memory and process management, scheduler,
    early boot filesystem.
  \item Back (Linux) and front (Ethos) xen drivers for enabling
    communication between Ethos domain and a Linux host
    across Xenbus.
  \end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Developer} & August 2005 - August 2007\\
    TabMobile Project, & \texttt{http://tablab.cs.uic.edu/\~{
    }tablab/tabmobile/}\\
  \end{tabular*}
  \begin{sitemize}
  \item Design and implementation of prototype core application
    for the Tabmobile Project, a research project
    focusing on applying state-of-the-art touch screen technology to
    refine a new teaching paradigm.
  \end{sitemize}

\item
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{Developer} & September 2004 - April 2005\\
    Project PSTool, &
    \texttt{http://www.sourceforge.net/projects/pstool}\\
  \end{tabular*}
  \begin{sitemize}
  \item Design and implementation of a parallel distributed (MPI) tool
    for calculating a one-sided power spectrum for
    electron-paramagnetic-resonance/laser
    spectroscopy research.
  \end{sitemize}
\end{itemize}

{\large \textbf{Skills}}
\begin{sitemize}
\item Specialties
\begin{sitemize}
\item Android, ARMv7, ACPI, algorithms, assembly, BIOS, boot loaders, C, C++, EDK2, low-level debugging support, device drivers, device emulation, emulation, firmware, IPC, kernel bring-up, kernel development, kernel porting, Linux kernel, low-level development, multithreading, .NET, NT kernel, os development, PCI, POSIX, system programming, system/network administration, SysV, SCSI, TCP/IP, Tiano Core, UEFI, virtual machines, virtualization, WDM, Win32, x86, x86-64, Xen
\end{sitemize}
\item Interests
\begin{sitemize}
\item Low-level, kernels, operating systems, design, algorithms, hard problems, virtualization, hypervisors, drivers, block storage, file systems, schedulers, debuggers, emulation.
\end{sitemize}
\end{sitemize}
\end{document}
